Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-04-20 main.Rmd
except in application section week-of-month removed

With two linear granularities $G$ and $H$, if $G$ *groups into* or *finer than* $H$ then $G$ is of lower order than $H$. For example, if the bottom granularity is day, then granularity week will have lower order than month since each week consist of fewer days than each month.

@@

\begin{table}[ht]
\centering
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
Quasi-circular granularity && Possible period lengths\\
\midrule
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24\times 31, 24\times 30, 24\times 29, 24\times 28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\caption{Examples of quasi-circular granularities relating two linear granularities with irregular mapping leading to several possible period lengths.}
\label{tab:quasi}
\end{table}

@@

Structurally empty combinations can arise due to the structure of the calendar or hierarchy. For example, let $C_i$ be day-of-month with 31 levels and $C_j$ be week-of-month with 5 levels. There will be $31\times 5=155$ sets $S_{k\ell}$ corresponding to possible combinations of $C_i$ and $C_j$. Many of these are empty. For example, $S_{1,5}$ is empty because the first day of the month can never correspond to the fifth week of the month. Hence the pair (day-of-month, week-of-month) is a clash.

>>>>

With two linear granularities $G$ and $H$, if $G$ *groups into* or *finer than* $H$ then $G$ is of lower order than $H$. For example, if the bottom granularity is hour, then granularity day will have lower order than week since each day consist of fewer hours than each week.

@@

\begin{table}[ht]
\centering
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
Quasi-circular granularity && Possible period lengths\\
\midrule
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24\times 31, 24\times 30, 24\times 29, 24\times 28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
\bottomrule
\end{tabular}
\caption{Examples of quasi-circular granularities relating two linear granularities with irregular mapping leading to several possible period lengths.}
\label{tab:quasi}
\end{table}

@@

Structurally empty combinations can arise due to the structure of the calendar or hierarchy. For example, let $C_i$ be day-of-month with 31 levels and $C_j$ be day-of-year with 365 levels. There will be $31\times 365=11315$ sets $S_{k\ell}$ corresponding to possible combinations of $C_i$ and $C_j$. Many of these are empty. For example, $S_{1,5}$ is empty because the first day of the month can never correspond to the fifth day of the year. Hence the pair (day-of-month, day-of-year) is a clash.
